---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DPH

<!-- badges: start -->
[![R build status](https://github.com/celehs/DPH/workflows/R-CMD-check/badge.svg)](https://github.com/celehs/DPH/actions)
<!-- badges: end -->

DPH provides functions to fit standard discrete proportional hazards (DPH) model and adjusted DPH models for time-to-event data with mismeasured outcomes.

## Installation

You can install the development version from [GitHub](https://github.com/celehs/DPH) with:

``` r
# install.packages("devtools")
devtools::install_github("celehs/DPH")
```

## Example

```{r setup}
library(DPH)
```

Here is a simulated example which shows you how to use DPH:

```{r example}
set.seed(1)
n <- 100
time <- sample(1:5, n, replace = TRUE)
status <- rbinom(n, 1, 0.5)
covariates <- rnorm(n)
```

Fit standard DPH model:

```{r model}
dph_fit0(time, status, covariates)
```

## References

- Evaluating Biomarkers using Panel Current Status Data with
Misclassication Errors. (Working Paper)

- Meier, A. S., Richardson, B. A., & Hughes, J. P. (2003). Discrete proportional hazards models for mismeasured outcomes. Biometrics, 59(4), 947–954. https://doi.org/10.1111/j.0006-341x.2003.00109.x

- [Complementary Log-Log Model for Interval-Censored Survival Times](https://documentation.sas.com/?cdcId=statcdc&cdcVersion=14.2&docsetId=statug&docsetTarget=statug_logistic_examples19.htm&locale=en#statug.logistic.logx12codea)
